Sub-10 Hz dark resonance at the cesium clock frequency induced by an optical frequency comb laser

### 2010-04-01 paper.tex
testing "units" package for units

%%% Units
%\newcommand{\unit}[1]{~\ensuremath{\, \mathrm{#1}}}
\usepackage{units}

@@

% Max of 600 characters for PRL, Rapid Comm abstracts.
\begin{abstract}
We used an optical frequency comb to resolve a dark state of
exceptionally narrow linewidth (\unit[5.6]{Hz}) in cesium gas buffered
with neon atoms, by precisely controlling the comb repetition rate.
The substantial pressure shift of the clock frequency expected
from the literature CW measurements was not observed. We
used optical Bloch-equations to interpret the experimental results. The
reported resonance has potential not only to enhance the
frequency discrimination of a microwave clock to the sub-10~Hz level,
but also to provide a link from the microwave time standard to the
optical frequency.
\end{abstract}

>>>>

%%% Units
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}

@@

% Max of 600 characters for PRL, Rapid Comm abstracts.
\begin{abstract}
We used an optical frequency comb to resolve a dark state of
exceptionally narrow linewidth (5.6\unit{Hz}) in cesium gas buffered
with neon atoms, by precisely controlling the comb repetition rate.
The substantial pressure shift of the clock frequency expected
from the literature CW measurements was not observed. We
used optical Bloch-equations to interpret the experimental results. The
reported resonance has potential not only to enhance the
frequency discrimination of a microwave clock to the sub-10~Hz level,
but also to provide a link from the microwave time standard to the
optical frequency.
\end{abstract}
